---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multsampsize

<!-- badges: start -->
[![R-CMD-check](https://github.com/alexpate30/multsampsize/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/alexpate30/multsampsize/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/alexpate30/multsampsize/graph/badge.svg)](https://app.codecov.io/gh/alexpate30/multsampsize)
<!-- badges: end -->

The goal of multsampsize is to estimate sample sizes for multinomial logistic regression models [@10.1177/09622802231151220].

## Installation

You can install the development version of multsampsize from [GitHub](https://github.com/) with:

```{r}
# pak::pak("alexpate30/multsampsize")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(multsampsize)
## basic example code
```

This can be used in the same way as `pmsampsize::pmsampsize` by specifying `type = "m"`. 

The number of outcome categories `K` must be specified. 

The number of expected events in each outcome category must be specified. Note, this is used to estimate the prevalence of each outcome category relative to eachother. Therefore, the absolute values are not important, just their relative values. These values can therefore be estimated from a previously published study, even if this study is of a different sample size to the study you are planning to implement.

One, and only one of nagrsquared, csrsquared and cstatistic must be specified. These must be vectors of length equal to the number of pairs of outcome categories. The order must be sequential, first in category k, then category r. For example, when `K = 3`, the elements must be as follows:

* Element 1: Pair(1,2); k = 1, r = 2.
* Element 2: Pair(1,3); k = 1, r = 3.
* Element 3: Pair(2,3); k = 2, r = 3.

When `K = 4`, the elements must be as follows:

* Element 1: Pair(1,2); k = 1, r = 2.
* Element 2: Pair(1,3); k = 1, r = 3.
* Element 3: Pair(1,4); k = 1, r = 4.
* Element 4: Pair(2,3); k = 2, r = 3.
* Element 5: Pair(2,4); k = 2, r = 4.
* Element 6: Pair(3,4); k = 3, r = 4.

One, and only one of `mult_nagrsquared_overall` and `mult_rsquared_overall` must be specified. The rsquared of a multinomial logistic regression model, `mult_rsquared_overall`, is rarely reported and may be difficult to pre-specify. It will therefore be common to specify `mult_nagrsquared_overall`

This first examples mimics the worked example from manuscript Pate et al.

```{r}
my_sampsize_calc <- pmsampsize_mult_general(type = "m",
                                            parameters = 17,
                                            shrinkage = 0.9,
                                            cstatistic = c(0.85, 0.92, 0.99, 0.95, 0.75, 0.95, 0.87, 0.87, 0.71, 0.82),
                                            ### New parameters
                                            K = 5,
                                            mult_n_events = c(2557, 186, 176, 467, 120),
                                            mult_nagrsquared_overall = 0.15)
```

The output contains the expected pairwise performance metrics (pertaining to criterion i), as well as the sample size for each criterion.

```{r}
my_sampsize_calc
```

Another random example:

```{r}
my_sampsize_calc <- pmsampsize_mult_general(type = "m",
                                            nagrsquared = c(0.15,0.15,0.15),
                                            parameters = 17,
                                            shrinkage = 0.9,
                                            ### New parameters
                                            K = 3,
                                            mult_n_events = c(50,100,150),
                                            mult_nagrsquared_overall = 0.15)
my_sampsize_calc
```
